A holographic approach to the six-dimensional superconformal index

### 2022-10-14 fivebranes/fact.tex
edits

We now formulate an expectation about the worldvolume theory on a stack of holomorphically twisted fivebranes.
Evidence for this description be given in the remaining parts of this paper, and we will formulate a more refined conjecture in the next section at the level of local operators.

>>>>

We now formulate an expectation about the worldvolume theory on a stack of holomorphically twisted fivebranes.
Evidence for this description will be given in the remaining parts of this paper, and we will formulate a more refined conjecture in the next section at the level of local operators.
